### 2010-12-28 Documentation/atropos/atropos.tex
ENH:  A few minor edits.
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@721 fd2da0a4-d968-48df-9cb5-d8c496287cbf
ENH:  A few minor edits.
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@722 fd2da0a4-d968-48df-9cb5-d8c496287cbf

OPTIONS: 
     -d, --image-dimensionality 2/3/4
     -i, --input-image inputImageFilename
     -x, --mask-image maskImageFilename
     -w, --weight-image weightImageFilename
     -s, --shrink-factor 1/2/3/4/...
     -c, --convergence [<numberOfIterations=50>,<convergenceThreshold=0.001>]
     -b, --bspline-fitting [splineDistance,<splineOrder=3>,<sigmoidAlpha=0.0>,
                           <sigmoidBeta=0.5>]
                           [initialMeshResolution,<splineOrder=3>,<sigmoidAlpha=0.0>,
                           <sigmoidBeta=0.5>]
     -t, --histogram-sharpening [<FWHM=0.15>,<wienerNoise=0.01>,<numberOfHistogramBins=200>]
     -o, --output [correctedImage,<biasField>]
     -h 
     --help 
\end{lstlisting} 
\end{command}
\subsubsection{Integration of N4 Bias Correction}
The typical segmentation processing pipeline begins with an intensity
normalization/bias correction step using the recently developed N4
algorithm \citep{Tustison2010} which is based on the popular
non-parametric nonuniformity intensity normalization (N3) introduced in \cite{Sled1998}.  It was previously mentioned that
several methods proposed in the literature have taken an integrative
view of the segmentation problem by incorporating an intrinsic bias
correction step into the actual workflow.  The
advancements introduced with N4 permit such an adaptive
integration with Atropos.  Recent demonstrations suggest improved
white matter segmentation produces better gain field estimates using
N3 \citep{Boyes2008}.  Thus, when performing 3-tissue segmentation, we
may opt to use, for instance, the posterior probability map of white matter at the current
iteration as a weighted mask for input to N4.  This is done by setting
the `{\ttfamily --weight-image}' option on the N4 command line call
(see Listing \ref{listing:n4}) to the posterior probability image
corresponding to the white matter produced as output in the Atropos
call, i.e. `{\ttfamily Atropos --output}'.  N4 is
currently being added as a standard part of the Insight ToolKit.  The
evaluation section will illustrate inclusion of Atropos, N4 and ANTs
in a brain processing pipeline.  An example of this procedure, using brainweb data with
40\% RF bias, is in figure~\ref{fig:bwebrf40}.  We supply the
information necessary to repeat this example in the script entitled
`{\ttfamily  atroposBwebRF40FigureExample.sh}' which is available in the ANTs toolkit's Atropos
documentation folder as of svn commit 711.
\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[width=6in]{Figures/bwebN4ex.pdf}
\end{tabular}
\caption{\baselineskip 12pt \small We combine N4 and Atropos by simple
sequential processing and apply to brainweb single-subject data with
40\% RF bias and 3\% noise.  The $\beta$ for the MRF term is, here,
$0.2$.  Slice 71 of the input data is in (a).  The initial K-means
($K=3$) segmentation is in panel (b).  We use the brain mask to guide
N4 bias correction and produce the image, shown in (c).  We repeat the
K-means segmentation, but with the N4 corrected image as input, and
produce the segmentation in (d).  The average 3-tissue Dice overlap of
result (b) is 0.906 while the average overlap for (d) is 0.954.
Arrows highlight a region of large before-after segmentation
discrepancy.}
\label{fig:bwebrf40}
\end{center}
\end{figure}

@@

initialization with MRF $\beta \in \{ 0.00 , 0.05 , 0.10 , 0.15 , 0.20
, 0.25 , 0.30 \}$ at each bias field.  We also feed the white matter

@@

correction.  Segmentation is then repeated, with the same parameters,

>>>>

OPTIONS: 
     -d, --image-dimensionality 2/3/4
     -i, --input-image inputImageFilename
     -x, --mask-image maskImageFilename
     -w, --weight-image weightImageFilename
     -s, --shrink-factor 1/2/3/4/...
     -c, --convergence [<numberOfIterations=50>,<convergenceThreshold=0.001>]
     -b, --bspline-fitting [splineDistance,<splineOrder=3>,<sigmoidAlpha=0.0>,
                           <sigmoidBeta=0.5>]
                           [initialMeshResolution,<splineOrder=3>,<sigmoidAlpha=0.0>,
                           <sigmoidBeta=0.5>]
     -t, --histogram-sharpening [<FWHM=0.15>,<wienerNoise=0.01>,<numberOfHistogramBins=200>]
     -o, --output [correctedImage,<biasField>]
     -h 
     --help 
\end{lstlisting} 
\end{command}
\subsubsection{Integration of N4 Bias Correction}
The typical segmentation processing pipeline begins with an intensity
normalization/bias correction step using the recently developed N4
algorithm \citep{Tustison2010} which is based on the popular
non-parametric nonuniformity intensity normalization (N3) introduced in \cite{Sled1998}.  It was previously mentioned that
several methods proposed in the literature have taken an integrative
view of the segmentation problem by incorporating an intrinsic bias
correction step into the actual workflow.  The
advancements introduced with N4 permit such an adaptive
integration with Atropos.  Recent demonstrations suggest improved
white matter segmentation produces better gain field estimates using
N3 \citep{Boyes2008}.  Thus, when performing 3-tissue segmentation, we
may opt to use, for instance, the posterior probability map of white matter at the current
iteration as a weighted mask for input to N4.  This is done by setting
the `{\ttfamily --weight-image}' option on the N4 command line call
(see Listing \ref{listing:n4}) to the posterior probability image
corresponding to the white matter produced as output in the Atropos
call, i.e. `{\ttfamily Atropos --output}'.  N4 is
currently being added as a standard part of the Insight Toolkit.  The
evaluation section will illustrate inclusion of Atropos, N4 and ANTs
in a brain processing pipeline.  An example of this procedure, using brainweb data with
40\% RF bias, is in figure~\ref{fig:bwebrf40}.  We supply the
information necessary to repeat this example in the script entitled
`{\ttfamily  atroposBwebRF40FigureExample.sh}' which is available in the ANTs toolkit's Atropos
documentation folder as of svn commit 711.
\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[width=6in]{Figures/bwebN4ex.pdf}
\end{tabular}
\caption{\baselineskip 12pt \small We combine N4 and Atropos by simple
sequential processing and apply to brainweb single-subject data with
40\% RF bias and 3\% noise.  The $\beta$ for the MRF term is, here,
$0.2$.  Slice 71 of the input data is in (a).  The initial K-means
($K=3$) segmentation is in panel (b).  We use the brain mask to guide
N4 bias correction and produce the image, shown in (c).  We repeat the
K-means segmentation, but with the N4 corrected image as input, and
produce the segmentation in (d).  The average 3-tissue Dice overlap of
result (b) is 0.906 while the average overlap for (d) is 0.954.
Arrows highlight a region of large before-after segmentation
discrepancy.}
\label{fig:bwebrf40}
\end{center}
\end{figure}

@@

initialization with MRF $\beta \in \{ 0.00 , 0.05 , 0.10 , 0.15 , 0.20, 
0.25 , 0.30 \}$ at each bias field.  We also feed the white matter

@@

correction.%
A comprehensive evaluation of N4 reported in \cite{Tustison2010} used the BrainWeb data set
to compare performance with the original N3 algorithm \cite{Sled1998}.
Segmentation is then repeated, with the same parameters,
